Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
Adding a response about relationship q/recommendations
Addresses #48

We will try to answer these questions through the analysis of questions and
answers in the two surveys. Eventually, what we want to obtain is a series of
recommendations to make a successful deployment of chatbot technologies (and, in
some cases, general instant messaging applications) in higher education.

>>>>

We will try to answer these questions through the analysis of questions and
answers in the two surveys. Eventually, what we want to obtain is a series of
recommendations to make a successful deployment of chatbot technologies (and, in
some cases, general instant messaging applications) in higher education\textcolor{blue}{; from the response to RQ1 and RQ4 we will try to recommend specific technologies or applications to be used in the classroom; the response to RQ2 and RQ3 will help us recommend chatbots features or specific platforms; and finally, from R3 we will also try to find best practices in the adoption of messaging platforms and they accompanying chatbots.}
